Determinism, Complexity, and Predictability in Computer Performance

### 2014-07-16 related.tex
few edits to end of related.tex

>>>>

They don't do real predictions and they don't use real-world data.

Also they had models so could generate as much data as needed to
perform their calculations.  Not practical in real data.

They never actually do prediction, just use FTLE as proxy.  This makes
general sense if you've got a deterministic system, but not stochastic
systems, where FTLEs don't reflect predictability.
